---
title: "Flo"
output: pdf_document
---

```{r}
sentiment <- vader_df(combined_df$text)
combined_df <- cbind (combined_df, sentiment["compound"])
```

## R Markdown

Filter for relevant movements

```{r}
movement_no_relevant_tweet_tesla <- (filter(tesla_df, relevant_tweet_posted==F))$movement
movement_relevant_tweet_tesla <- (filter(tesla_df, relevant_tweet_posted==T))$movement
movement_tesla <- tesla_df$movement
movement_no_tweet_tesla <- (filter(tesla_df, tweet_posted==FALSE))$movement
movement_tweet_tesla <- (filter(tesla_df, tweet_posted==TRUE))$movement
```

TESLA: 
comparison: do stock-movements differ significantly from each other when Musk tweets something (movement_tweet_tesla) vs. when Musk tweets nothing (movement_no_tweet_tesla)? 
first step: testing if variances of the two groups are equal, which they are not -> using Welch-Test
```{r}
var_hom <- var.test(movement_tweet_tesla, movement_no_tweet_tesla)
var_hom
```
t-test for independent samples to test hypothesis 1: Elon Musks tweets have an impact on tesla-stock-movements. 
Hypothesis 1 could not be verified: Tesla-Stock-Movements do not differ in dependency of Elon Musks Tweets (t = -0.26, ns)
```{r}
t.test(movement_tweet_tesla, movement_no_tweet_tesla, var.equal = F, alternative = "two.sided")
```

creating values in order to plot the results of the independent sampled t-test
```{r}
# Means and create SEM
mean_movement_tweet_tesla <- mean(movement_tweet_tesla)
mean_movement_no_tweet_tesla <- mean(movement_no_tweet_tesla)
SEM_movement_tweet_tesla <- sd(movement_tweet_tesla)/sqrt(length((movement_tweet_tesla)))
SEM_movement_no_tweet_tesla <- sd(movement_no_tweet_tesla)/sqrt(length((movement_no_tweet_tesla)))
SEM_movement_no_tweet_tesla
SEM_movement_tweet_tesla
mean_movement_tweet_tesla
mean_movement_no_tweet_tesla
```
plotting the results via ggplot2
```{r}
#create sample data
tesla_stock_move <- data.frame(name=c("movement_tweet_tesla","movement_no_tweet_tesla"),
                  value=c(mean_movement_tweet_tesla, mean_movement_no_tweet_tesla),
                  SEM=c(SEM_movement_tweet_tesla, SEM_movement_no_tweet_tesla)
)

#create barplot 
ggplot(tesla_stock_move, aes(name, value))+
  geom_col(size=5)+
  geom_errorbar( aes(x=name, ymin=value-SEM, ymax=value+SEM), width=0.5, colour="orange", alpha=0.9, size=0.5)
```
histogram of our descriptive tesla-movement-data 
```{r}
hist(movement_tweet_tesla)
hist(movement_no_tweet_tesla)
```
NEXT ANALYSIS TESLA
comparison: do stock-movements differ significantly from each other when Musk tweets something relevant (movement_relevant_tweet_tesla) vs. when Musk tweets nothing relevant (movement_no_tweet_tesla)? 

first step: testing if variances of the two groups are equal, which they are
```{r}
var_hom <- var.test(movement_relevant_tweet_tesla, movement_no_relevant_tweet_tesla)
var_hom
```

t-test for independent samples to test hypothesis 2: Elon Musks relevant tweets have an impact on tesla-stock-movements. 
Hypothesis 1 could not be verified: Tesla-Stock-Movements do not differ in dependency of Elon Musks relevant Tweets (t = 0.41, ns)

```{r}
t.test(movement_relevant_tweet_tesla, movement_no_relevant_tweet_tesla, var.equal = T, alternative = "two.sided")
```

creating values in order to plot the results of the independend sampled t-test
```{r}
# Means and create SEM
mean_movement_relevant_tweet_tesla <- mean(movement_relevant_tweet_tesla)
mean_movement_no_relevant_tweet_tesla <- mean(movement_no_relevant_tweet_tesla)
SEM_movement_relevant_tweet_tesla <- sd(movement_relevant_tweet_tesla)/sqrt(length((movement_relevant_tweet_tesla)))
SEM_movement_no_relevant_tweet_tesla <- sd(movement_no_relevant_tweet_tesla)/sqrt(length((movement_no_relevant_tweet_tesla)))
SEM_movement_no_relevant_tweet_tesla
SEM_movement_relevant_tweet_tesla
mean_movement_relevant_tweet_tesla
mean_movement_no_relevant_tweet_tesla
```

plotting the results 
```{r}
#create sample data
tesla_stock_move <- data.frame(name=c("relevant tweet","irrelevant tweet"),
                  value=c(mean_movement_relevant_tweet_tesla, mean_movement_no_relevant_tweet_tesla),
                  SEM=c(SEM_movement_relevant_tweet_tesla, SEM_movement_no_relevant_tweet_tesla)
)

#create barplot 
ggplot(tesla_stock_move, aes(name, value, fill=name))+#
  geom_col(size=5)+
  geom_errorbar( aes(x=name, ymin=value-SEM, ymax=value+SEM), width=0.5, colour="orange", alpha=0.9, size=0.5)+
  ggtitle("Plot two sample t-Test: Tesla-Stock-Movement")+
  xlab("Groups")+ 
  ylab("Mean Movement")
```

TESLA REGRESSION

```{r}
write.table(tweets_df, file="data/Tweets_df.csv", sep=";")
write.table(tesla_df, "data/Tesla_df.csv",  sep=";")
write.table(bitcoin_df, "data/Bitcoin_df.csv",  sep=";")
sentiment_tesla_df <- read.xlsx2("data/LM_Tesla.xlsx", 1, header=TRUE)
sentiment_bitcoin_df <- read.xlsx2("data/LM_bitcoin_new.xlsx", 1, header=TRUE)
sentiment_bitcoin_df <-sentiment_bitcoin_df %>% replace(.=="ERROR", NA)
sentiment_tesla_df <-sentiment_tesla_df %>% replace(.=="ERROR", NA)
```

Regression: Predictor = sentiment of Musk-Tweets, Criterion = movement of stock-price on day of tweet 
adjusted-R = 
```{r}
relevant_sentiment_tesla <- na.omit(sentiment_tesla_df)
linear_Model_tesla_test <- lm(movement_in_percent_NEW~as.numeric(as.character(movement_relevant_compound)), data=relevant_sentiment_tesla)
linear_Model_tesla_test
summary(linear_Model_tesla_test)
plot(relevant_sentiment_tesla$movement_relevant_compound, relevant_sentiment_tesla$movement_in_percent_NEW, xlab="Sentiment", ylab="Movement", col="darkblue", pch=16, main="Simple Linear Regression")
abline(linear_Model_tesla_test)
```

New DF: per Relevant Tweets we assign movement and sentiment (compound).

```{r}
no_zero_sentiment_tesla_df <- relevant_sentiment_tesla %>% replace(.=="0", NA)
no_zero_sentiment_tesla_df <- na.omit(no_zero_sentiment_tesla_df)
linear_Model_tesla_test2 <- lm(movement_in_percent_NEW~as.numeric(as.character(movement_relevant_compound)), data=no_zero_sentiment_tesla_df)
linear_Model_tesla_test2
summary(linear_Model_tesla_test2)
plot(no_zero_sentiment_tesla_df$movement_relevant_compound, no_zero_sentiment_tesla_df$movement_in_percent_NEW, xlab="Sentiment", ylab="Movement", col="darkblue", pch=16, main="Simple Linear Regression")
abline(linear_Model_tesla_test2)
```

```{r}
hist(residuals(linear_Model_tesla_test2))
```



################################################################################################################
BITCOIN 

```{r}
movement_no_relevant_tweet_bitcoin <- (filter(bitcoin_df, relevant_tweet_posted==0))$movement
movement_relevant_tweet_bitcoin <- (filter(bitcoin_df, relevant_tweet_posted==1))$movement
movement_bitcoin <- bitcoin_df$movement
movement_no_tweet_bitcoin <- (filter(bitcoin_df, tweet_posted==FALSE))$movement
movement_tweet_bitcoin <- (filter(bitcoin_df, tweet_posted==TRUE))$movement
```

testing the assumption of equal variances -> var-test not significant, calculate t-test 
```{r}
varianz_hom_all_btc <- var.test(movement_tweet_bitcoin, movement_no_tweet_bitcoin)
varianz_hom_all_btc
```

Testing Hypothesis 3: Elon Musk-Tweets do have an impact on Bitcoin-Courses. 
Hypothesis 3 can not be verified, movement in Btc-Cours does not differ depending on tweets from Elon Musk (t = -1.4, ns)
```{r}
t.test(movement_tweet_bitcoin, movement_no_tweet_bitcoin, var.equal = T, alternative = "two.sided")
```

creating values in order to plot the results of the independent sampled t-test
```{r}
# Means and create SEM
mean_movement_tweet_bitcoin <- mean(movement_tweet_bitcoin)
mean_movement_no_tweet_bitcoin <- mean(movement_no_tweet_bitcoin)
SEM_movement_tweet_bitcoin <- sd(movement_tweet_bitcoin)/sqrt(length((movement_tweet_bitcoin)))
SEM_movement_no_tweet_bitcoin <- sd(movement_no_tweet_bitcoin)/sqrt(length((movement_no_tweet_bitcoin)))
SEM_movement_no_tweet_bitcoin
SEM_movement_tweet_bitcoin
mean_movement_tweet_bitcoin
mean_movement_no_tweet_bitcoin
```

plotting the results 
```{r}
#create sample data
bitcoin_move <- data.frame(name=c("movement_tweet_bitcoin","movement_no_tweet_bitcoin"),
                  value=c(mean_movement_tweet_bitcoin, mean_movement_no_tweet_bitcoin),
                  SEM=c(SEM_movement_tweet_bitcoin, SEM_movement_no_tweet_bitcoin)
)

#create barplot 
ggplot(bitcoin_move, aes(name, value, fill=name))+
  geom_col(size=5)+
  geom_errorbar( aes(x=name, ymin=value-SEM, ymax=value+SEM), width=0.5, colour="orange", alpha=0.9, size=0.5)+
  ggtitle("Plot of the two sample t-Test")+
  xlab("Groups")+ 
  ylab("Mean Movement")



```

NEXT ANALYSIS BITCOIN
comparison : do course-movements differ significantly from each other when Musk tweets something relevant (movement_relevant_tweet_bitcoin) vs. when Musk tweets nothing relevant (movement_no_tweet_bitcoin)? 

first step: testing if variances of the two groups are equal, which they aren´t -> Welch-Test 
```{r}
var_hom <- var.test(movement_relevant_tweet_bitcoin, movement_no_relevant_tweet_bitcoin)
var_hom
```
Welch-Test in order to test Hypothesis 4: Relevant Tweets from Elon Musk have an impact on Bitcoin-Courses. Hypothesis 4 can not be verified, relevant Tweets do not differ from unrelevant tweets (t = -0.42, ns)
```{r}
t.test(movement_relevant_tweet_bitcoin, movement_no_relevant_tweet_bitcoin, var.equal=F, alternative = "two.sided")
```

creating values in order to plot the results of the independent sampled t-test
```{r}
# Means and create SEM
mean_movement_relevant_tweet_bitcoin <- mean(movement_relevant_tweet_bitcoin)
mean_movement_no_relevant_tweet_bitcoin <- mean(movement_no_relevant_tweet_bitcoin)
SEM_movement_relevant_tweet_bitcoin <- sd(movement_relevant_tweet_bitcoin)/sqrt(length((movement_relevant_tweet_bitcoin)))
SEM_movement_no_relevant_tweet_bitcoin <- sd(movement_no_relevant_tweet_bitcoin)/sqrt(length((movement_no_relevant_tweet_bitcoin)))
SEM_movement_no_relevant_tweet_bitcoin
SEM_movement_relevant_tweet_bitcoin
mean_movement_relevant_tweet_bitcoin
mean_movement_no_relevant_tweet_bitcoin
```

plotting the results 

```{r}
#create sample data
bitcoin_move <- data.frame(name=c("relevant_tweet","irrelevant_tweet"),
                  value=c(mean_movement_relevant_tweet_bitcoin, mean_movement_no_relevant_tweet_bitcoin),
                  SEM=c(SEM_movement_relevant_tweet_bitcoin, SEM_movement_no_relevant_tweet_bitcoin)
)

#create barplot 
ggplot(bitcoin_move, aes(name, value, fill=name))+
  geom_col(size=5)+
  geom_errorbar( aes(x=name, ymin=value-SEM, ymax=value+SEM), width=0.5, colour="orange", alpha=0.9, size=0.5)+
  ggtitle("Plot Welch two sample t-Test: Bitcoin-Movement")+
  xlab("Groups")+ 
  ylab("Mean Movement")
```
#####################################DESCRIPTIVE#####STATISTICS#################################################
TESLA
```{r}
mean(tesla_df$movement)
sd(tesla_df$movement)
hist(tesla_df$movement)

plotNormalHistogram( tesla_df$movement, prob = FALSE,
                      main = "Normal Distribution TESLA",
                      length = 1000 )
```

BITCOIN
```{r}
mean_btc <- mean(bitcoin_df$movement)
sd_btc <- sd(bitcoin_df$movement)

plotNormalHistogram( bitcoin_df$movement, prob = FALSE,
                      main = "Normal Distribution BTC",
                      length = 1000 )
```

